---
title: "simulation"
author: "renyan"
date: "2022/4/11"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 模拟数据生成

```{r}
rm(list = ls(all = TRUE))
ls()
setwd("D:/Ryanna/RUC_courses/Y1_2/Group/code")
library(Matrix)
library(MASS)
library(fmrs)
source("sim.r")

n <- 120                         # The sample size
p <- 10                           # The dimension of x
q <- 5                         # The dimension of z
pq <- q*p                        # The dimension of each sample
# dim_nonzero_x <- 2                         # The dimension of non-zero coefficients of x
# dim_nonzero_z <- 4                        # The dimension of non-zero coefficients of z
# E.cat <- 2                       # The dimension of non-zero coefficients of z
mu <- 2                      # The signal intensity of non-zero coefficients
balance <- T                     # Balanced/Imbalanced subgroup
gr_num_main <- 2                     # The number of rough subgroup 
gr_num_sub <- 4                       # The number of refined subgroup 
hier_struc <- list(c(1,2),c(3,4))  # Hierarchical subgroup structure
# sd.epsi<-0.5                     # The residual error
# corZX <- F                       # Correlated/Uncorrelated X and Z
intercorr0<-"AR1"                # The correlation structure of Z
signal_its <- 2 # signal intensity
K <- gr_num_sub
set.seed(9)

# ------------ Necessary parameters to support algorithm implementation --------
comb_pair <- combn(K,2)
H_3 <- kronecker(Matrix(t(apply(comb_pair,2,dMatrixFun)),sparse = T),bdiag(diag(pq)))
H_1 <- kronecker(Matrix(t(apply(comb_pair,2,dMatrixFun)),sparse = T),bdiag(diag(p)))
H_2 <- kronecker(Matrix(t(apply(comb_pair,2,dMatrixFun)),sparse = T),bdiag(diag(q)))
one_matrix_w <- bdiag(rep(list(rep(1,pq)),(K*(K-1)/2)))
one_matrix_x <- bdiag(rep(list(rep(1,q)),(K*(K-1)/2)))
one_matrix_z <- bdiag(rep(list(rep(1,p)),(K*(K-1)/2)))

# ------------ Generate the regression coefficients -----------
# coef_main_value <- c(signal_its,-signal_its)
# coef_sub_value <- c(1.5*signal_its,0.5*signal_its,-0.5*signal_its,-1.5*signal_its)
coef_main_value <- c(signal_its,0.5*signal_its)
coef_sub_value <- c(2*signal_its,1.5*signal_its,1*signal_its,0.5*signal_its)
if(balance){pr_sub<-rep(1/gr_num_sub,gr_num_sub)}else{pr_sub<-c(1/6,1/6,1/3,1/3)}

# true main groups & subgroups
ci <- ci_generate(n, pr_sub, hier_struc)
ci_main <- ci$ci_main
ci_sub <- ci$ci_sub
ci_sim <- rep(0, n)
for(i in 1:K){
  ci_sim[ci_sub[[i]]] <- i
}

# true coefficients
coef_true <- generate_coef_true(n, p, q, ci_main, ci_sub, coef_main_value, coef_sub_value)

# ------------ Generate data ------------ 
whole.data <- generate_sim_data(n, p, q, coef_true, cotype_x="AR_E", cotype_z="AR_E")
# whole.data$data_y <- whole.data$data_y + 100
```

# Description

```{r}
library(ggplot2)
library(corrplot)
```

- 响应变量分布

```{r}
ggplot(data.frame(y = whole.data$data_y), aes(x = y)) +
  geom_histogram() +
  theme_minimal()
```

- 自变量（$X, Z, W$）相关系数矩阵  
    - 之前实验发现，使用 `fmrs` 包进行初始化时，如果传入的协变量之间有强相关性，则模型返回结果为空，故在此先观察分析自变量之间的相关性。

```{r}

# corrplot(cor(whole.data$X))
# corrplot(cor(whole.data$Z))
# corrplot(cor(whole.data$W))
corrplot(cor(whole.data$X_all))
```




# Model

## Initialization


### flexmix

- 给的组别数比较大时，`flexmix` 包不一定什么时候出现 na，在没有出现空值的时候也会 no convergence
- 每次运行结果不稳定
- 给的组别数比较合适时，会收敛
- 只能对主效应进行拟合，加入交互项后总是得到 NaN loglikelihood，原因不详

```{r}
library("flexmix")
K_up <- 2
# 无交互项模型
fm <- flexmix(whole.data$data_y ~ whole.data$X_main, k = K_up,
               control = list(iter.max = 100, verbose = 3))
fm
```

```{r}
summary(fm)
```


```{r}
# 系数分布
coef_matrix <- matrix(c(fm@components$Comp.1[[1]]@parameters$coef,
                      fm@components$Comp.2[[1]]@parameters$coef), ncol = 2)
yhat <- cbind(1, whole.data$X_main) %*% coef_matrix
yhat_df <- data.frame(yhat)
library(ggplot2)
ggplot(yhat_df) +
  geom_histogram(aes(x = X1), alpha = 0.6) +
  geom_histogram(aes(x = X2), alpha = 0.6, fill = "blue") +
  theme_minimal()
```


### RobMixReg

```{r}
library(RobMixReg)
res <- MLM(ml.method = 'hrmr',
           x = whole.data$X_all,
           y = whole.data$data_y, 
           nc = K_up)
# save(file = "robmixreg2.RData", res)
load("robmixreg2.RData")
```



```{r}
res$coff
table(res$cluMem)
compPlot(type='block', res=res)
res$BIC
```


```{r}
# hist(res$res$posterior[[1]])
```

```{r}
# 得到不同类别的参数
res$res$lmList
```


### fmrs

> 截距项处理，系数相同问题

- 解决问题：各类别系数相同
    - 参数初始化重要，不能 `rep`，考虑随机生成
    - Hierarchical 文章初始值设置为 (1,1,...,1,-1,-1,...,-1)，仿照此会将只能分为两组

```{r}
int_rm <- TRUE
K_up <- 4
as <- matrix(1, nrow = p+q+pq+1, ncol = K_up)
if(int_rm){ as[1,] <- 0 }

# 初始化参数
# coef_rough_init <- rep(1, K_up * (p+q+pq+1))
# coef_rough_init <- c(rep(1, K_up * (p+q+pq+1) %/% 2), 
#                      rep(0.5, K_up * (p+q+pq+1) - K_up * (p+q+pq+1) %/% 2))
coef_rough_init <- rnorm(K_up * (p+q+pq+1))
res.mle <- fmrs.mle(
  y = whole.data$data_y,
  x = whole.data$X_all,
  delta = rep(0, length(whole.data$data_y)),
  nComp = K_up,
  disFamily = "norm",
  initCoeff = coef_rough_init,
  initDispersion = rep(1, K_up),
  initmixProp = rep(1 / K_up, K_up),
  nIterNR = 200,
  activeset = as
)
# summary(res.mle)
coefficients(res.mle)
```

- `fmrs.tunsel`: The maximizer of penalized Log-Likelihood depends on selecting a set of good tuning parameters which is a rather thorny issue. We choose a value in an equally spaced set of values in $(0, \lambda_{max})$ for a pre-specified λmax that maximize the component-wise BIC

$\hat{\lambda}_{k}=\operatorname{argmax}_{\lambda_{k}} B I C_{k}\left(\lambda_{k}\right)=\operatorname{argmax}_{\lambda_{k}}\left\{\ell_{k, n}^{c}\left(\hat{\Psi}_{\lambda_{k}, k}\right)-\left|d_{\lambda_{k}, k}\right| \log (n)\right\},$

where $d_{\lambda_{k}, k}=\left\{j: \hat{\beta}_{\lambda_{k}, k j} \neq 0, j=1, \ldots, d\right\}$ is the active set excluding the intercept and $\left|d_{\lambda_{k}, k}\right|$ is its size. This approach is much faster than using an nComp by nComp grid to select the set $\boldsymbol{\lambda}$ to maximize the penallized Log-Likelihood.

```{r}
res.lam <- fmrs.tunsel(y = whole.data$data_y, 
                       x = whole.data$X_all, 
                       delta = rep(0, length(whole.data$data_y)),
                       nComp = K_up, 
                       disFamily = "norm",
                       initCoeff = c(coefficients(res.mle)),
                       initDispersion = dispersion(res.mle),
                       initmixProp = mixProp(res.mle),
                       penFamily = "mcp", 
                       nIterNR = 200,
                       activeset = as
)
res.lam@lambPen
```

- `fmrs.varsel`: Provides variable selection and penalized MLE for Finite Mixture of Regression (FMR) Models. The penalized likelihood of a finite mixture of the models is written as

$$
\tilde{\ell}_{n}(\boldsymbol{\Psi})=\ell_{n}(\boldsymbol{\Psi})-\mathbf{p}_{\boldsymbol{\lambda}_{n}}(\boldsymbol{\Psi})
$$

where 

$$
\mathbf{p}_{\boldsymbol{\lambda}_{n}}(\boldsymbol{\Psi})=\sum_{k=1}^{K} \pi_{k}^{\alpha}\left\{\sum_{j=1}^{d} p_{\lambda_{n, k}}\left(\beta_{k j}\right)\right\}
$$

```{r}
res.var <- fmrs.varsel(y = whole.data$data_y, 
                       x = whole.data$X_all, 
                       delta = rep(0, length(whole.data$data_y)),
                       nComp = ncomp(res.mle), 
                       disFamily = "norm",
                       initCoeff = c(coefficients(res.mle)),
                       initDispersion = dispersion(res.mle),
                       initmixProp = mixProp(res.mle),
                       penFamily = "mcp",
                       lambPen = slot(res.lam, "lambPen"), 
                       nIterNR = 200
)
res.var@dispersion
res.var@mixProp
```


```{r}
fmr_res <- c()
fmr_weight_ci <- apply(res.var@weights,1,which.max)
fmr_res_ci <- apply(abs(res.var@residuals),1,which.min) 
for (i in 1:n) {
  fmr_res[i] <- res.var@residuals[i, fmr_res_ci[i]]
}
fmr_var <- sqrt(sum(fmr_res^2))
fmr_bic <- res.var@BIC

fmr_coe <- res.var@coefficients
if(int_rm){ fmr_coe <- res.var@coefficients[-1,]  }

# 针对类别，每个系数拉长作为列向量
coef_init <- as.vector(fmr_coe)
```

```{r}
table(ci_sim, fmr_weight_ci)
table(ci_sim, fmr_res_ci)
prop.table(table(fmr_weight_ci))
prop.table(table(fmr_res_ci))
```







