---
title: "Untitled"
author: "renyan"
date: "2022/2/25"
output: 
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(prettydoc)
```

```{r}
setwd("D:/Ryanna/RUC_courses/Y1_2/Group/code")
source("ref/codes-Hierarchical-2021-1-10/Simulation/function.R")
source("ref/codes-Hierarchical-2021-1-10/Simulation/sim-func.R")
```

```{r}
library(Matrix)
library(MASS)
library(fmrs)
```

```{r}
n <- 120                         # The sample size
q <- 5                           # The dimension of x
p <- 10                          # The dimension of z
pp <- q+p                        # The dimension of each sample
S_E <- 2                         # The dimension of non-zero coefficients of x
S_GE <- 4                        # The dimension of non-zero coefficients of z
E.cat <- 2                       # The dimension of non-zero coefficients of z
beta00 <- 2                      # The signal intensity of non-zero coefficients 原文中的 mu
balance <- F                     # Balanced/Imbalanced subgroup
gr.main <- 2                     # The number of rough subgroup 
gr.GE <- 4                       # The number of refined subgroup 
num_main <- list(c(1,2),c(3,4))  # Hierarchical subgroup structure
sd.epsi<-0.5                     # The residual error
corZX <- F                       # Correlated/Uncorrelated X and Z
intercorr0<-"AR1"                # The correlation structure of Z
```

```{r}
# ------------ Necessary parameters to support algorithm implementation --------
sample.index <- combn(n,2)
a.matrix <- kronecker(Matrix(t(apply(sample.index,2,dMatrixFun)),sparse = T),bdiag(diag(pp)))
a.matrix.main <- kronecker(Matrix(t(apply(sample.index,2,dMatrixFun)),sparse = T),bdiag(diag(q)))
a.matrix.GE <- kronecker(Matrix(t(apply(sample.index,2,dMatrixFun)),sparse = T),bdiag(diag(p)))
one.matrix <- bdiag(rep(list(rep(1,pp)),(n*(n-1)/2)))
one.matrix.main <- bdiag(rep(list(rep(1,q)),(n*(n-1)/2)))
one.matrix.GE <- bdiag(rep(list(rep(1,p)),(n*(n-1)/2)))
```

```{r}
# ------------ Generate the regression coefficients -----------
beta_main.vec <- c(-beta00,beta00)
beta_GE.vec <- c(-1.5*beta00,-0.5*beta00,1.5*beta00,0.5*beta00)
if(balance){pr_GE<-rep(1/gr.GE,gr.GE)}else{pr_GE<-c(1/6,1/6,1/3,1/3)}
group.num <- group_GE(n, pr_GE=pr_GE, num_main=num_main)
group.num_main <- group.num$group.num_main
group.num_GE <- group.num$group.num_GE
Beta0 <- Generatebeta(n, q, p, group.num_main, group.num_GE, beta_main.vec, beta_GE.vec, sparse=T, S_GE=S_GE, S_E=S_E)
beta.true.list <- Beta0$beta.true.list
```

```{r}
# ------------ Generate data ------------ 
whole.data <- GenerateData(n, p, q, beta.true.list,
  maincorr = "AR_E", intercorr = intercorr0,
  sd.epsi = sd.epsi, corZX = corZX, E.cat = E.cat
)
```

```{r}
# 生成参数初始值
beta.init.list <- gen_int_beta(n, p, q, whole.data)
beta.init <- beta.init.list$beta.init
lambda <- genelambda.obo()
result <- tuning.lambda(lambda, whole.data, n, q, p, beta.init)
index.list <- evaluation.tuning(n,q,p, result$admmres, result$abic.n, result$admmres2, result$abic.n2, Beta0, gr.GE=gr.GE, result$bic.var)
index.list$err.s
```

0. `beta.init.list <- gen_int_beta(n, p, q, whole.data)` 的细节

```{r}
subgroup=c(2,4)
gr.init=5
lambda.min=0.0001

pp<-p+q
n<-length(whole.data$data_y)
fmr.bic<-c()
fmr.res0<-c()
res.mle0.list<-list()
nC <- 2
# 初始系数为 -1 或 1
b00 = c(rep(-1,(nC*pp+nC)/2),rep(1,nC*pp+nC-floor((nC*pp+nC)/2)))
res.mle <- fmrs.mle(y = whole.data$data_y, x =whole.data$data_x,
                    delta = rep(0,length(whole.data$data_y)),
                          nComp =nC, disFamily = "norm",
                          # initCoeff = rnorm(nC*pp+nC),
                          initCoeff = b00,
                          initDispersion = rep(1,nC),
                          initmixProp = rep(1/nC, nC),nIterNR = 200)
res.lam <- fmrs.tunsel(y = whole.data$data_y, x =whole.data$data_x,delta =
                         rep(0,length(whole.data$data_y)),
                             nComp =nC, disFamily = "norm",
                             initCoeff = c(coefficients(res.mle)),
                             initDispersion = dispersion(res.mle),
                             initmixProp = mixProp(res.mle),
                             penFamily = "adplasso",nIterNR = 200)
res.var <- fmrs.varsel(y = whole.data$data_y, x =whole.data$data_x, delta =
                         rep(0,length(whole.data$data_y)),
                             nComp = ncomp(res.mle), disFamily = "norm",
                             initCoeff=c(coefficients(res.mle)),
                             initDispersion = dispersion(res.mle),
                             initmixProp = mixProp(res.mle),
                             penFamily = "adplasso",
                             lambPen = slot(res.lam, "lambPen"),nIterNR = 200)
res.mle0<-res.var
fmr.res=apply(abs(res.mle0@residuals),1,which.min)
fmr.resj=c()
for (jj in 1:n) {
  fmr.resj[jj]=res.mle0@residuals[jj,fmr.res[jj]] # 两个类别中，按照残差最小的类别拟合得到的残差
}
sqrt(sum(fmr.resj^2)) # 残差平方和
res.mle0@BIC # BIC
fmr.coe<-res.mle0@coefficients[-1,] # 除去截距项，其他系数
# fmr.w 每个样本属于哪个类别，按照权重
fmr.w<-apply(res.mle0@weights,1,which.max) # res.mle0@weights 为每个样本属于每个类别的概率 
# fmr.r 每个样本属于哪个类型，按照残差平方和
fmr.r<-apply(abs(res.mle0@residuals),1,which.min)

# weight
beta.int.fmr<-list()
for (i in 1:n) {
  beta.int.fmr[[i]]<-as.matrix(as.numeric(fmr.coe[,fmr.w[i]])) # 只用所属类别的系数
}
beta.init=do.call(rbind,beta.int.fmr)
```


1. `result <- tuning.lambda(lambda, whole.data, n, q, p, beta.init)` 的细节

```{r}
lambda1 = lambda$lambda1[[1]]
lambda2 = lambda$lambda2[[1]]
# 此处省略参数循环过程，只看某一组参数
ad<-ADMM(n, q, p, whole.data, beta.init, lambda1, lambda2, merge.all=F) # ->
```

1.1 `ad<-ADMM(n, q, p, whole.data, beta.init, lambda1, lambda2, merge.all=F)` 的细节

```{r}
# 默认参数复制
p_y=1
iter.max=50
epsi=0.1
gam.mcp=3 # The regularization parameter in MCP, the default setting is 3 笔记里的a
penal.para=1 # The penalty parameter in ADMM algorithm, the default setting is 1. 笔记里的k
merge.all=F
data.total <- whole.data

pp=q+p
main.n=c(1:q) # 主效应列索引
GE.n=setdiff(1:pp,main.n) # 次效应列索引
a.main.n = sort(rep((0:(n-1))*pp,q))+main.n # 长度 600=n*q
a.GE.n = sort(rep((0:(n-1))*pp,p))+GE.n # 长度 1200=n*p
d.main.n =sort(rep((0:(n*(n-1)/2-1))*pp,q)) + main.n # 长度 35700=n(n-1)/2 * q
d.GE.n = sort(rep((0:(n*(n-1)/2-1))*pp,p)) + GE.n # 长度 71400=n(n-1)/2 * p

cova<-data.total$data_x
data.response<-data.total$data_y

row_vec<-vector(mode="list",length=n)
for(i5 in 1:n){
  row_vec[[i5]]<-matrix(cova[i5,],1,pp)
}
cova_diag<-bdiag(row_vec) # dim 120*1800=n*n(p+q)
```

```{r}
#################################### Initialize beta #########################################
# group
eta.init<-a.matrix%*%beta.init # dim n(n-1)/2*(q+p) * 1 列向量
gamma.init<-Matrix(0,nrow=p_y,ncol=pp*n*(n-1)/2,sparse = T) # dim 1 * n(n-1)/2*(q+p) 行向量
```

```{r}
# iteration
iter<-1
# coe
beta.est.list<-vector(mode="list",length=iter.max);beta.est.list[[iter]]<-beta.init
# differences of coe
eta.est.list<-vector(mode="list",length=iter.max);eta.est.list[[iter]]<-eta.init
# the dual variables
gamma.est.list<-vector(mode="list",length=iter.max);gamma.est.list[[iter]]<-gamma.init

# 以下为循环内容
iter <- 2
beta.est.list[[iter]] <- solve(t(cova_diag) %*% cova_diag + penal.para * t(a.matrix) %*% a.matrix) %*%
  (t(cova_diag) %*% data.response - t(a.matrix) %*% t(gamma.est.list[[iter - 1]]) + penal.para * (t(a.matrix) %*% eta.est.list[[iter - 1]]))

eta.i = a.matrix%*%beta.est.list[[iter]]
gamma.i = gamma.est.list[[iter-1]]
eta.tem1<-eta.i+t(gamma.i)/penal.para
eta.tem1.main<-as.matrix(eta.tem1[d.main.n,],sparse=T)
eta.tem1.GE<-as.matrix(eta.tem1[d.GE.n,],sparse=T)
eta.i1<-eta.i

# 2-norm
eta.tem2norm.main<-sqrt(t(one.matrix.main)%*%(eta.tem1.main^2))
eta.tem2norm.GE<-sqrt(t(one.matrix.GE)%*%(eta.tem1.GE^2))
eta.tem2norm<-sqrt(eta.tem2norm.GE^2 + eta.tem2norm.main^2)

# all:non-shrinkage & main:non-shrinkage
num_n_n<-which(eta.tem2norm > gam.mcp*lambda1 & eta.tem2norm.main > gam.mcp*lambda2)

# all:shrinkage & main:non-shrinkage
vu.coe<-apply(1-lambda1/penal.para/eta.tem2norm,1,function(x) max(x,0)) / (1-1/(gam.mcp*penal.para))
vv<- vu.coe * eta.tem2norm.main
num_s_n<-which(eta.tem2norm <= gam.mcp*lambda1 & vv > gam.mcp*lambda2)

# all:non-shrinkage & main:shrinkage
vv.coe<-apply(1-lambda2/penal.para/eta.tem2norm.main,1,function(x) max(x,0)) / (1-1/(gam.mcp*penal.para))
ww<-sqrt(eta.tem2norm.GE^2 + ( vv.coe * eta.tem2norm.main)^2)
num_n_s<-which(ww > gam.mcp*lambda1 & eta.tem2norm.main <= gam.mcp*lambda2)

# all:shrinkage & main:shrinkage
num_s_s<-setdiff(1:(n*(n-1)/2),Reduce(union,list(num_n_n,num_s_n,num_n_s)))

if(length(num_n_n)<2){
  num_n_n2<-which(rowSums(as.matrix(one.matrix[,num_n_n]))!=0)
}else{num_n_n2<-which(rowSums(one.matrix[,num_n_n])!=0)}
if(length(num_s_n)<2){
  num_s_n2<-which(rowSums(as.matrix(one.matrix[,num_s_n]))!=0)
}else{num_s_n2<-which(rowSums(one.matrix[,num_s_n])!=0)}
if(length(num_n_s)<2){
  num_n_s2<-which(rowSums(as.matrix(one.matrix[,num_n_s]))!=0)
}else{num_n_s2<-which(rowSums(one.matrix[,num_n_s])!=0)}
if(length(num_s_s)<2){
  num_s_s2<-which(rowSums(as.matrix(one.matrix[,num_s_s]))!=0)
}else{num_s_s2<-which(rowSums(one.matrix[,num_s_s])!=0)}

# all:non-shrinkage & main:non-shrinkage
if(length(num_n_n2) > 0){eta.i1[num_n_n2,]<-eta.i[num_n_n2,]}

# all:shrinkage & main:non-shrinkage
num = num_s_n; num2 = num_s_n2;
if(length(num) > 0){
  eta.tem3<-as.matrix(vu.coe[num])
  eta.tem4<-as.vector(apply(eta.tem3, 1, function(x) rep(x,pp)))
  eta.i1[num2,]<-eta.tem4*eta.i[num2,]
}

# all:non-shrinkage & main:shrinkage
num = num_n_s; num2 = num_n_s2;
if(length(num) > 0){
  num.main = num2[sort(rep((1:length(num)-1)*pp,q)) + main.n]
  num.GE = num2[sort(rep((1:length(num)-1)*pp,p)) + GE.n]
  eta.tem3<-as.matrix(vv.coe[num])
  eta.tem4<-as.vector(apply(eta.tem3, 1, function(x) rep(x,q)))
  eta.i1[num.main,]<-eta.tem4*eta.i[num.main,]
  eta.i1[num.GE,]<-eta.i[num.GE,]
}

# all:shrinkage & main:shrinkage
num = num_s_s; num2 = num_s_s2;
if(length(num) > 0){
  num.main = num2[sort(rep((1:length(num)-1)*pp,q)) + main.n]
  num.GE = num2[sort(rep((1:length(num)-1)*pp,p)) + GE.n]
  eta.i0norm<-sqrt(t(one.matrix)%*%(eta.est.list[[iter-1]]^2))
  eta.i0norm.main<-sqrt(t(one.matrix.main)%*%(eta.est.list[[iter-1]][d.main.n,]^2))
  mcp.u<-mcp_d(eta.i0norm[num],lambda1,gam.mcp)/penal.para/(eta.i0norm[num]+10^(-7))
  mcp.v<-mcp_d(eta.i0norm.main[num],lambda2,gam.mcp)/penal.para/(eta.i0norm.main[num]+10^(-7))
  eta.tem3.main<-as.matrix(mcp.u+mcp.v)
  eta.tem3.GE<-as.matrix(mcp.u)
  eta.tem4.main<-as.vector(apply(eta.tem3.main, 1, function(x) rep(x,q)))
  eta.tem4.GE<-as.vector(apply(eta.tem3.GE, 1, function(x) rep(x,p)))
  eta.i1[num.main,]<-eta.i[num.main,]/(1+eta.tem4.main)
  eta.i1[num.GE,]<-eta.i[num.GE,]/(1+eta.tem4.GE)
  eta.i1[abs(eta.i1) < 10^(-9)]=0
}

eta.est.list[[iter]] = eta.i1
gamma.est.list[[iter]]<-gamma.est.list[[iter-1]]+penal.para*t(a.matrix%*%beta.est.list[[iter]]-eta.est.list[[iter]])
eps.group = sqrt(sum((a.matrix%*%beta.est.list[[iter]]-eta.est.list[[iter]])^2))

if(eps.group<epsi){
  break
}

beta.est.list[iter-1]<-list(NULL)
eta.est.list[iter-1]<-list(NULL)
gamma.est.list[iter-1]<-list(NULL)
```
























